For this assignment, the author was instructed to build a competitive co-evol\-utionary search algorithm for Pac-Man.
In the prior assignment, 2B, Pac-Man's intelligence was extended by using a genetic programming search algorithm.
To build on this the current iteration has the Ghosts' utilizing a genetic programming search algorithm. 
The two populations will compete against each other, and in theory, get better as the generations go on.
However, there can be certain situations that can cause undesirable effects which are discussed later.

The Ghosts are given the same algorithms that Pac-Man has access to.
Their choices for parent selection algorithms are fitness proportional selection and over selection and for survival selection: truncation, k-tournament without replacement.
Via the configuration file, one can change both $\lambda$, $\mu$, $k$, mutation rates, and parsimony pressure for Pac-Man and the Ghosts separately.

This paper starts with the methodology section which explains the custom parts of the author's EA framework.
Additionally, differences relative to assignment 2B are explained as to not re-explain the entire framework to the grader.
Following the methodology section is a section explaining the author's experiments and how they were setup and ran.
This is useful so the graders can produce the same results as the author if the need arises.
The results of these experiments are located in the result section.
Here all the experiment's data is listed in graphical formats along with statistical analysis of the data sets.
After the results are stated there will be a discussion that contains the author's understanding of the data.
Along with this is a brief discussion of the CIAO plots produced by the experiments.
Following the discussion section will be the conclusion which will wrap up the paper.
